---
title: "R Markdown"
---

This is an R Markdown file. You can use it to take notes and run code. For example, you can write your name on the line below. Try it: 



```{r}
# You can write code in chunks that look like this.
# This chunk uses the code plot(cars) to plot a data set.
# To run the code click the Green play button to the right. Try it!
plot(cars)
```

Good job! The results of a code chunk will appear beneath the chunk. You can click the x above the results to make them go away, but let's not do that.

You can open a new R Markdown file by going to **File > New File > R Markdown...**. Then click OK.

# Adding chunks

To add a new chunk, press *Cmd+Option+I* (*Ctrl+Alt+I* on Windows), or click the *Insert* button at the top of this document, then select *R*. 
Try making a code chunk below:



Good job! For today, you should place all of your R code inside of code chunks.

```{r}
# You can click the downward facing arrow to the left of the play button to run
# every chunk above the current code chunk. This is useful if the code in your
# chunk depends on the code in previous chunks, for example, if your chunk 
# uses an object or data set made in a previous chunk.
# Sys.Date()
```

Did you notice the green lines in the code chunk above? They are *code comments*, lines of text that R ignores when it runs the code. R will treat everything that appears after `#` on a line as a code comment. As a result, if you run the chunk above, nothing will happen—it is all code comments (and that's fine)!

Remove the `#` on the last line of the chunk above and then rerun the chunk. Can you tell what `Sys.Date()` does?

# Text formatting

Have you noticed the funny highlighting that appears in this document? R Markdown treats text surrounded by *asterisks*, **double asterisks**, and `backticks` in special ways. It is R Markdown's way of saying that these words are in

- *italics*
- **bold**, and
- `code font`

`*`, `**`, and \` are signals used by a text editing format known as `markdown`. R Markdown uses `markdown` to turn your plain looking .Rmd documents into polished reports. Let's give that a try.

# Reports

When you click the `knit` button at the top of an R Markdown file (like this one), R Markdown generates a polished copy of your report. It:

1. Transforms all of your markdown cues into actual formatted text (e.g. bold text, italic text, etc.)
2. Reruns all of your code chunks in a clean R session and appends the results to the finished report.
3. Saves the finished report alongside your .Rmd file

Click the *knit* button at the top of this document or press *Cmd+Shift+K* (*Ctrl+Shift+K* on Windows) to render the finished report. The RStudio IDE will open the report so you can see its contents. For now, our reports will be HTML files. Try clicking *Knit* now.

Good job! You'll learn more about R Markdown throughout the day, but now let's look at how to access the parts of R that we want to use the most: the Tidyverse!

# R Packages

The code chunk below runs a function from the ggplot2 package, which we will learn about today. Uncomment the code (delete the `#`) and run the chunk. What happens?

```{r}
# ggplot(data = diamonds) + geom_point(aes(x = carat, y = price))
```

Uh-oh! This is an error message. It means something has gone wrong. In general, if you see an error message that says `could not find function` it means that you misspelled the function name or you have not loaded the package that the function comes in.

Let's look at what packages are and how you can load one.
